Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2014-11-03 ms.tex
some comments

\label{sec:sample}

Our sample includes 61 early-type galaxies from
\citetalias{WangMerritt:2004a}, as represent a subset of a larger
sample of \citet{FaberTremaine+:1997a} with Hubble WFPC2 imaging.  We
focus on elliptical galaxies because we are interested in isolating
SMBHs fed by the steady mass loss from the relatively old stellar
population, instead of fresh gas flowing into the sphere of influence
from larger scales.

@@

The SMBH accretion rate is simply given by the integrated mass loss rate interior to the stagnation radius (equation~[\ref{eq:q}]), 
\begin{eqnarray}
  \dot{M} &=& \frac{\eta \Menc(\rs)}{\th} \nonumber \\
&\approx&
  \begin{cases}
    1.6 \times 10^{-3}  M_{\bullet,8}^{1.9}
    v_{500}^{-4}  \eta \Msun \, \pyear& \text{core} \\
    3.4 \times 10^{-3} \Mbheight^{1.4}
    v_{500}^{-2}  \eta \Msun \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:mdot_analytic}
\end{eqnarray}
where the numerical estimates again assume that $M_{\bullet} \gg M_{\star}$ at the stagnation radius.  Equation (\ref{eq:mdot_analytic}) predicts that $\dot{M}$ should increase with SMBH mass at fixed heating $v_{500}$, but decreases rapidly with increased heating.

@@

For each solution we calculate the accretion rate $\dot{M}$ onto the
SMBH in units of the Eddington accretion rate $\dot{M}_{\rm edd}
\equiv L_{\rm edd}/0.1 c^{2}$, where $L_{\rm edd} \approx 1.4\times
10^{46}M_{\bullet,8}$ erg s$^{-1}$.  Figure~\ref{fig:mdot_mass} shows
$\dot{M}/\dot{M}_{\rm edd}$ as a function of $\Mbh$ for different
values of $\vwO =$ 200, 500 and 1000 km s$^{-1}$.

>>>>

\label{sec:sample}
%AG:It is unclear whether if/how the Nuker profile will show up in
%this parametrized study.
Our sample includes 61 early-type galaxies from
\citetalias{WangMerritt:2004a}, as represent a subset of a larger
sample of \citet{FaberTremaine+:1997a} with Hubble WFPC2 imaging.  We
focus on elliptical galaxies because we are interested in isolating
SMBHs fed by the steady mass loss from the relatively old stellar
population, instead of fresh gas flowing into the sphere of influence
from larger scales.

@@

The SMBH accretion rate is simply given by the integrated mass loss
rate interior to the stagnation radius (equation~[\ref{eq:q}]), 
%AG: Should we have separate cores and cusps? Or just write a general
%relationship in terms of gamma?
\begin{eqnarray}
  \dot{M} &=& \frac{\eta \Menc(\rs)}{\th} \nonumber \\
&\approx&
  \begin{cases}
    1.6 \times 10^{-3} M_{\bullet,8}^{1.9}
    \chi^{-4} v_{500}^{-4}  \eta \Msun \, \pyear& \text{core} \\
    3.4 \times 10^{-3} \Mbheight^{1.4} \chi^{-2}
    \chi^{-2} v_{500}^{-2}  \eta \Msun \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:mdot_analytic}
\end{eqnarray}

@@

For each solution we calculate the accretion rate $\dot{M}$ onto the
SMBH in units of the Eddington accretion rate $\dot{M}_{\rm edd}
\equiv L_{\rm edd}/0.1 c^{2}$, where $L_{\rm edd} \approx 1.4\times
10^{46}M_{\bullet,8}$ erg s$^{-1}$.  Figure~\ref{fig:mdot_mass} shows
$\dot{M}/\dot{M}_{\rm edd}$ as a function of $\Mbh$ for different
values of $\vwO =$ 150, 300 and 600 km s$^{-1}$.
